%  sample input file for using the NASA.cls LaTeX class
%  this distribution is handy for formatting TM, TP, CR, etc.
%
%  $Id: sample.tex,v 1.18 2009/08/10 17:22:22 wawood Exp $

%  next 2 lines pull in the NASA.cls file, put options between []
\documentclass[]             % options: RDPonly, coveronly, nocover
{NASA}                       %   plus standard article class options


%  Fill in the following categories between the braces {}
\title{Avionics for Low-Cost High-Altitude Balloon Science Platforms}
\author{J. C. Chin J. McNatt, A. Roberts and Rocket U} % list all the author names for the RDP

\AuthorAffiliation{Jeffrey Chin, Jeremiah McNatt, Anthony Roberts \\  % list the authors
  Glenn Research Center, Cleveland, OH\\[10pt]   % with affiliations
  %Doug Astler, Kristen Bury,  Deborah Goodenow, Steven Korn, 
  %Jeremiah McNatt, \\ 
  %Justin Niehaus,  Anthony Roberts, Amanda Stevenson, Fransua Thomas  \\ 
    % list the authors
  %Glenn Research Center, Cleveland, OH\\[10pt]
  }
\NasaCenter{Glenn Research Center\\Cleveland, OH 44135-3127}
\Type{TM}                    % TM, TP, CR, CP, SP, TT
\SubjectCategory{64}         % two digit number
\LNumber{12456}              % Langley L-number
\Number{217743}              % Report number
\Month{02}                   % two digit number
\Year{2015}                  % four digit number
\SubjectTerms{CFD, grid}     % 4-5 comma separated words
\Pages{10}                   % all the pages from the front to back covers
\DatesCovered{10/2013--2/2014}              % 10/2000--2/2014
\ContractNumber{}            % NAS1-12345
\GrantNumber{}               % NAG1-1234
\ProgramElementNumber{}
\ProjectNumber{}             % NCC1-123
\TaskNumber{}                % Task 123
\WorkUnitNumber{}            % 123-45-67-89
\SupplementaryNotes{}
\Acknowledgment{This paper is based on work done by the
pilot Rocket University training program.
Special thanks to my peers in the cohort, subject-matter 
experts, Paul Bartollotta and Rochelle Ghallagher.}

\abstract{ High-altitude balloons (HABs) have become popular as
educational and scientific platforms for planetary research.
This document outlines key components for missions
where low cost and rapid development are desired.
As an alternative to ground-based vacuum and thermal testing,
these systems can be flight tested at comparable costs.
Communication, solar, space, and atmospheric sensing experiments often require
environments where ground-level can be challenging or
impossible in certain cases. When performing HAB research
the ability to monitor the status of the platform and
gather data is key for both scientific and recoverability aspects of the mission.
A few turn-key platform solutions are outlined that
leverage rapidly evolving open-source engineering ecosystems.
Rather than building custom components from scratch,
these recommendations attempt to maximize 
simplicity and cost of a HAB platforms to make launches more accessible to everyone.
}   % suggested 200 words

\usepackage{minted} %syntax highlighting
\usepackage{color} %syntax highlighting
\usepackage{graphicx}
\usepackage{changepage}
\usepackage{amsmath} %math equations
\usepackage{url}
\usepackage{subfiles} %break up document into subfiles
\usepackage{hyperref} %hyperlinks
\usepackage{courier} %courier font for variable names
\usepackage{cleveref} %section references
\usepackage[all]{hypcap} %figure references point to top of figure (must come after hyperref)
\usepackage{wrapfig}
\usepackage{subcaption}
\usepackage{float} %override image placement

%these seemed to be necessary with minted... not sure what they do..
\makeatletter
\color{black}
\let\default@color\current@color
\makeatother
\restylefloat{figure} %override image placement

%reference appendix
\crefname{appsec}{Appendix}{Appendices}
\begin{document}

\tableofcontents
\listoffigures
\listoftables

\subfile{avionics}

\bibliographystyle{unsrt} %sorted by appearence, consider using natbib?
\bibliography{bibliography}

\subfile{appendix}

\end{document}